### 2016-10-03 FrontBackmatter/Introduction.tex
Simplify configuration and add higher resolution images in introduction
Some more repo clean up
Finally get openright, right
Always link acronyms back to list of acronyms

\begin{figure}[tb]
\centering
\includegraphics[width=.8\textwidth]{qc-axes.png}
\caption[Pictorial depiction of the concept of \emph{model chemistries}.]{
Pictorial depiction of the concept of \emph{model chemistries} as the
three dimensions of quantum chemistry.\autocite{Pople1999-gt, Saue2011-qg}
Reproduced from \noparcite[ref.][]{Norman2011-ad} with permission from the PCCP Owner Societies.
}
\label{fig:RQC-axis}
\end{figure}

@@

The description of the ideas and methods at the basis of quantum
chemistry will be the subject of Chapter \ref{ch:QM}.
I will put emphasis on the methods that have been relevant in the work
presented in this dissertation. Section \ref{sec:mqm} discusses some of the
ideas of quantum many-body theory relevant to quantum chemistry. Section
\ref{sec:mean-field} introduces the workhorses of quantum chemistry
\acrlong*{HF} and \acrlong*{KS} \acrlong*{DFT}.
The \acrlong*{MBPT} and \acrlong*{CC} rungs on the methodology axis will
be discussed in Sections \ref{sec:mbpt} and \ref{sec:coupled-cluster},
respectively.

\section*{The Problem of Solvation or Taming Complexity with Models}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\textwidth]{multiscale_models-landscape.png}
\caption[From quantum mechanical to multiscale models]{
Pictorial depiction of the transition from quantum mechanical to
multiscale models for the aqueous solvation of \emph{para}-nitroaniline.
Leftmost panel: a fully quantum mechanical cluster model.
Upper central panel: a quantum/classical discrete (explicit) model.
Lower central panel: a quantum/classical continuum (implicit) model.
Rightmost panel: a quantum/classical mixed explicit/implicit model.
Picture reproduced courtesy of Dr. Stefano Caprasecca (MoLEcoLab, Università di Pisa).}
\label{fig:qm-to-multiscale}
\end{figure}

While both models treat the molecular degrees of freedom at the quantum
mechanical level, their approach to the microscopic description of the
degrees of freedom of the environment differs:
\begin{itemize}
 \item
   \emph{Discrete} (or \emph{explicit}) models explicitly treat those
   degrees of freedom.
   This is either achieved by a cheaper quantum mechanical
   method\autocite{Vreven2006-gx} or by \gls{MM}.\autocite{Senn2009-sk}
   In the latter approach, commonly dubbed \acrshort{QM}/\acrshort{MM}, the \acrshort{MM}
   region can either be polarizable\autocite{Mennucci2013-go,
   Olsen2010-wa, Lipparini2011-rd} or non
   polarizable. While the former method allows for mutual polarization
   between the \acrshort*{QM} and \acrshort*{MM} subsystems, the latter
   treats the \acrshort*{MM} region as fixed.
 \item
   \emph{Continuum} (or \emph{implicit}) models completely remove the degrees
   of freedom of the environment from the model, replacing them with a
   structureless continuum.
   Its effect is described, classically, \emph{via} its bulk
   properties.\autocite{Onsager1936-wf, Miertus1981-mm}
\end{itemize}

@@

\begarrowthought{The concepts of systematic improvability and theoretical model
chemistries} are the foundations for the successful practice of quantum
chemistry.
A balanced description of electron correlation is often necessary
to achieve accurate enough results in the computation of molecular
properties.\autocite{Lee1995-pw, Helgaker2004-oz, Tajti2004-ye}
The cost-effective treatment of electron correlation is a challenging
problem and a very active line of research in the field.
\Acrlong*{DFT} approaches are cheap and widespread, but their general
accuracy is hard to assess. \Acrlong*{MBPT} and \acrlong*{CC} approaches
are more robust in this respect, albeit at an increased computational
cost.

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=.8\textwidth]{model-chem.pdf}
\caption[Pictorial depiction of the concept of \emph{model chemistries}.]{
Pictorial depiction of the concept of \emph{model chemistries} as the
three dimensions of quantum chemistry.\autocite{Pople1999-gt, Saue2011-qg}
Reproduced from \noparcite[ref.][]{Norman2011-ad} with permission from the PCCP Owner Societies.
}
\label{fig:RQC-axis}
\end{figure}

@@

The description of the ideas and methods at the basis of quantum
chemistry will be the subject of Chapter \ref{ch:QM}.
I will put emphasis on the methods that have been relevant in the work
presented in this dissertation. Section \ref{sec:mqm} discusses some of the
ideas of quantum many-body theory relevant to quantum chemistry. Section
\ref{sec:mean-field} introduces the workhorses of quantum chemistry
\acrlong{HF} and \acrlong{KS} \acrlong{DFT}.
The \acrlong{MBPT} and \acrlong{CC} rungs on the methodology axis will
be discussed in Sections \ref{sec:mbpt} and \ref{sec:coupled-cluster},
respectively.

\section*{The Problem of Solvation}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\textwidth]{multiscale_models-landscape.pdf}
\caption[From quantum mechanical to multiscale models]{
Pictorial depiction of the transition from quantum mechanical to
multiscale models for the aqueous solvation of \emph{para}-nitroaniline.
Leftmost panel: a fully quantum mechanical cluster model.
Upper central panel: a quantum/classical discrete (explicit) model.
Lower central panel: a quantum/classical continuum (implicit) model.
Rightmost panel: a quantum/classical mixed explicit/implicit model.
Picture reproduced courtesy of Dr. Stefano Caprasecca
(MoLEcoLab, Università di Pisa).}
\label{fig:qm-to-multiscale}
\end{figure}

While both models treat the molecular degrees of freedom at the
quantum
mechanical level, their approach to the microscopic description of the
degrees of freedom of the environment differs:
\begin{itemize}
 \item
   \emph{Discrete} (or \emph{explicit}) models explicitly treat those
   degrees of freedom.
   This is either achieved by a cheaper quantum mechanical
   method\autocite{Vreven2006-gx} or by \gls{MM}.\autocite{Senn2009-sk}
   In the latter approach, commonly dubbed \acrshort{QM}/\acrshort{MM}, the \acrshort{MM}
   region can either be polarizable\autocite{Mennucci2013-go,
   Olsen2010-wa, Lipparini2011-rd} or non
   polarizable. While the former method allows for mutual polarization
   between the \acrshort{QM} and \acrshort{MM} subsystems, the latter
   treats the \acrshort{MM} region as fixed.
 \item
   \emph{Continuum} (or \emph{implicit}) models completely remove the degrees
   of freedom of the environment from the model, replacing them with a
   structureless continuum.
   Its effect is described, classically, \emph{via} its bulk
   properties.\autocite{Onsager1936-wf, Miertus1981-mm}
\end{itemize}

@@

\begarrowthought{The concepts of systematic improvability and theoretical model
chemistries} are the foundations for the successful practice of quantum
chemistry.
A balanced description of electron correlation is often necessary
to achieve accurate enough results in the computation of molecular
properties.\autocite{Lee1995-pw, Helgaker2004-oz, Tajti2004-ye}
The cost-effective treatment of electron correlation is a challenging
problem and a very active line of research in the field.
\Acrlong*{DFT} approaches are cheap and widespread, but their general
accuracy is hard to assess. \Acrlong*{MBPT} and \acrlong{CC} approaches
are more robust in this respect, albeit at an increased computational
cost.
